---
title: "Keras logistic regression"
author: "Rob Walker"
output: html_document
---

# Titanic dataset
- This is a classification problem with 2 target classes (survived and died)

```{r}
knitr::opts_chunk$set(echo = TRUE)
df <- read.csv("titanic.csv")
library(ggplot2); library(cowplot); library(keras)

use_session_with_seed(19)
```

# Logistic regression
- similar to linear regression but with a dichotomous target (2 levels)
- logistic regression estimates the log odds (p/1-p) as a linear combination of feature variables
- select titanic variables survived and pclass
- remove missing data
- spineplot the relationship
- one hot encode pclass
- run glm(y~x,family="binomial")

```{r}
train = na.omit(df[,c("survived","pclass")])
y_train = train$survived
spineplot(factor(survived)~factor(pclass), data=train)

x_train <- model.matrix(~as.factor(pclass),data = train)[,2:3] # one hot encode pclass
colnames(x_train) <- c("class2","class3")

summary(glm_model <- glm(y_train ~ x_train, family = "binomial"))
```

# Keras
- Run a logistic model

```{r}
lr = .1
epochs = 100

model <- keras_model_sequential() %>%
    layer_dense(units = 1, activation = "sigmoid", 
                input_shape =  dim(x_train)[2])

model %>% compile( loss = "binary_crossentropy", 
                   optimizer = optimizer_adam(lr = lr, decay = lr/epochs),
                   metrics = 'accuracy')
model

history <- model %>% fit(x = x_train, y = y_train, verbose = 0, epochs = epochs)
plot(history)
```

# Compare model results
- glm vs Keras

```{r}
get_weights(model) # weights from Keras
model %>% evaluate(x_train, y_train, verbose = 0) # keras training accuracy

glm_model$coefficients[1:3] # weights from glm
fitted.results <- predict(glm_model,newdata=data.frame(x_train),type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)
print(paste('GLM accuracy',1-mean(fitted.results != train$survived)))

```

# Summary
- A logistic model is a special case of a neural network
- To make a logistic model we use a sigmoid activation, binary crossentropy loss, and a single output node which requires 3 weights (intercept/bias and 2 slopes/weights)
